Nail: A practical interface generator for data formats

### 2014-08-14 paper/osdi14/design.tex
cite data languages

Transformations need to be carefully written, because they can escape Nail's security and introduce
bugs. However, as we will show in \S\ref{s:eval-effort}, Nail transformations are much shorter than
hand-written parsers and many formats can be represented with just the provided transforms

>>>>

Transformations need to be carefully written, because they can escape Nail's security and introduce
bugs. However, as we will show in \S\ref{s:eval-effort}, Nail transformations are much shorter than
hand-written parsers and many formats can be represented with just the transformations in the
standard library.

### 2014-08-14 paper/osdi14/impl.tex
cite data languages

% The source code of our implementation, together with the examples described in
% \S\ref{s:eval} are available on GitHub at \url{https://github.com/jbangert/nail}.

@@

\paragraph{Defense-in-Depth.}

Security exploits often rely on raw inputs being present in memory, for example to include
shell-code or crafted stack frames for ROP-attacks in padding fields\cite{shotgun-parser} or the
application executing a controlled sequence of heap allocations and de-allocations to place
specific data at predictable addresses\cite{jp-advanced, vudo-malloc}. Because the rest of the
application or even Nail's generated code may contain memory corruption bugs, Nail
carefully handles memory allocations as defense-in-depth to make exploiting such vulnerabilities harder.

>>>>

The source code of our implementation, together with the examples described in
\S\ref{s:eval} are available on GitHub at \url{https://github.com/jbangert/nail}.

@@

\XXX[Add API here]
\paragraph{Defense-in-Depth.}

Security exploits often rely on raw inputs being present in memory~\cite{shotgun-parser}, for example to include
shell-code or crafted stack frames for ROP~\cite{phrack58:4-nergal}-attacks in padding fields or the
application executing a controlled sequence of heap allocations and de-allocations to place
specific data at predictable addresses~\cite{jp-advanced, vudo-malloc}. Because the rest of the
application or even Nail's generated code may contain memory corruption bugs, Nail
carefully handles memory allocations as defense-in-depth to make exploiting such vulnerabilities harder.

### 2014-08-14 paper/osdi14/relwk.tex
cite data languages

Closely related work has been done at Bell Labs with the PacketTypes
system~\cite{mccann2000packet}.  However, PacketTypes works only as a
parser, not as an output generator, and does not support the expressive
power of parsing expression grammars (PEGs), but rather implements a
C-like structure model enhanced with length fields and constraints.
PacketTypes also cannot handle complicated encodings such as compressed
data, which are supported by Nail's stream transforms.

>>>>

Closely related work has been done in the field of data description languages, for example
PacketTypes~\cite{mccann2000packet} and DataScript~\cite{DataScript}. However, PacketTypes works
only as a parser, not as an output generator. Data description languages typically are not as
expressive as parsing expression grammars (PEGs), but rather implement a C-like structure model
enhanced with length fields and constraints. These systems also cannot handle complicated encodings
such as compressed data, which are supported by Nail's stream transforms.
